---
title: "Report 2"
author: "Barbara Chen"
date: "2023-06-06"
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

In this report, I analyzed the differences between search terms (coffee table, nightstand, living room table, etc.) used to gather the data. I also analyzed the differences between products shown on the first and second page of each search term. Lastly, I analyzed the size and color/material of different products.

The goal of this report is to see if there are certain factors or features of a product that are associated with high revenue.

In the previous report, I did not find any relationship between price and sales and price and revenue. However, I found that \$90\~\$160 was a good price range. Thus, for this report, instead of comparing an individual product's price and revenue, I decided a better approach was to group the products based on price and revenue and compare the groups.

There are 4 revenue groups which are based on the quartiles. The products with revenue in the lower 25% is grouped into q1; 25%\~50% is grouped into q2, and so on.

There are 2 price groups. Products with prices below \$90 is group 1; \$90\~\$160 is group 2, and the rest is group 3.

## Conclusion

### Search Term:

1.  Despite being the most popular search term, 'coffee table' has pretty average revenue.
2.  'Living room table' and 'nightstand' have the highest percentage of products in the higher revenue range.
3.  About 30% of the products in 'living room table' is above \$90, while only about 20% of the products in 'nightstand' is above \$90.

### Size:

1.  'Nightstand', 'side table', 'end table', 'bedside table', and 'accent table' tend to be on the smaller side (D+W+H: 40 and 60 inches).
2.  'Coffee table' is on the larger side (D+W+H: 70\~80 inches).
3.  'Living room table' has the widest range of dimension (D+W+H: 50 and 80 inches).
4.  'Sofa table' leans the biggest (D+W+H: 80\~100 inches).
5.  Size had no observable effect on revenue. In general, average girth is around 50\~80 inches.

### Pages:

1.  In general, the first page of each search term shows more cheaper items than the second page. This is especially true for 'coffee table'.
2.  In general, the first page does not show as many recent products. However, the degree varies according to the search term.
3.  The reviews for page 1 and 2 are similar.

### Colors:

1.  The most popular colors in descending order are brown/black, brown, black, white, grey. These color groups appeared in every single search term.
2.  Although grey and grey/gold were only 5th and 6th most popular, the products in these color had higher revenue. This could be an indication that the color grey could be a good choice.


## Recommendations

1.  If planning to release a product in the \$90 to \$160 price range, living room table is a good reference. Compared to other search terms, its contains more products in the higher revenue groups. However, compared to other search terms, the first page of 'living room table' shows fewer recent products.
2.  The most common color/material is brown/wood or wood+metal frame. In other words, there is a lot of competition. Instead, grey may be a good option. There are fewer products in grey, but still common enough to be seen in every search term. Moreover, compared to the other colors, grey has higher revenue.
3.  In general, it is best to avoid what is the most common. We see that the most popular categories don't necessarily generate high revenue. For example, 'coffee table' is the most popular search term, but it actually has the lowest revenue in comparison. Another good example is the colors brown and brown/black. Despite being the most popular, they also don't have the best revenue.

```{r load libraries, include=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(dplyr)
library(pivottabler)
```

```{r load data, include = FALSE}
options(scipen = 999)

curr_path <- here()

df_names <- c("coffee_table",
              "nightstand",
              "side_table",
              "end_table",
              "bedside_table", 
              "sofa_table",
              "living_room_table",
              "accent_table")

paths <- vector("character", length(df_names))

for (i in 1:length(df_names)) {
  paths[i] = paste0(curr_path, "/data/cleaned/", df_names[i], "_cleaned.csv")
}

# store the data frames into a list
df_list <- list()
df_list <- lapply(paths, read_csv)
names(df_list) <- df_names

# read table specs (product dimension and colors)
tables_specs <- read.csv(paste0(curr_path, "/data/cleaned/final_product_details.csv"))
tables_specs <- tables_specs[, -c(1, 2, 4)]

```

```{r process data, include = FALSE}
# change the first column of all data frames to ranking, and add column which indicates which search term it appeared under
for (i in 1:length(df_list)) {
  df_list[[i]] <- mutate(df_list[[i]], search_term = paste0(i, '-', names(df_list[i])))
  df_list[[i]] <- rename(df_list[[i]], ranking = "...1")
}

# separate the package dimension into three columns
df_list <- lapply(df_list, function(df) {
  df %>% separate(dimensions, c("package_dim_1",
                                "package_dim_2",
                                "package_dim_3"), sep = 'x') %>% 
    transform(package_dim_1 = as.numeric(package_dim_1),
            package_dim_2 = as.numeric(package_dim_2),
            package_dim_3 = as.numeric(package_dim_3)) %>% 
    mutate(package_girth = package_dim_1 + package_dim_2 + package_dim_3)
})


# merge two table specs and individual data frames
df_list <- lapply(df_list, function(df) {
  df <- merge(df, tables_specs, by= c('asin'))
})

# since the search term is now its own column, we can combine all the data frames into a big one
all_df <- bind_rows(df_list) %>% arrange(ranking)

# examine the duplicates
dup <- all_df[duplicated(all_df$asin), ]
```

```{r transform data, include = FALSE}
# duplicate items will be removed after comparing individual search terms. 
# all_df <- all_df[!duplicated(all_df$asin), ]


all_df <- all_df %>% mutate(page = case_when(ranking < 48 ~ 1, TRUE ~ 2), log_rev = log(revenue))

# convert creation date to years and months
all_df <- all_df %>% mutate(creation_year = year(creation_date), creation_month = month(creation_date, label = TRUE), days_since_creation = as.integer((difftime('2023-06-02', creation_date, units = "days"))))

# add price groups and revenue groups
rq <- quantile((all_df %>% filter(!is.na(revenue)))$revenue)

all_df <- all_df %>% mutate(price_group = case_when(price <= 90 ~ '1',
                                                    (price > 90 & price <= 160) ~'2',
                                                    TRUE ~'3'),
                            rev_group = case_when(revenue <= rq[2] ~ 'q1',
                                                  revenue > rq[2] & revenue <= rq[3] ~ 'q2',
                                                  revenue > rq[3] & revenue <= rq[4] ~ 'q3',
                                                  revenue > rq[4] ~ 'q4',
                                                  TRUE ~ NA))
# add volume...
all_df <- all_df %>% mutate(vol_in = depth_in * width_in * height_in, 
                        package_vol = package_dim_1 * package_dim_2 * package_dim_3)

# df <- all_df %>% select(-c(product_details, url, image_url, fees, active_sellers_number, images, buy_box))

# rev_df -- all NA revenue removed
rev_df <- all_df %>% filter(!is.na(revenue))
```

## 1 Search Terms

### 1.1 Price

```{r message=FALSE}
ggplot(rev_df, aes(x=search_term, fill = price_group)) + 
  geom_bar(stat="count", position = position_fill(reverse = TRUE)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n=10) ) +
  coord_flip() +
  scale_fill_brewer(palette=5) +
  labs(title = "Price Groups of Search Terms", y = "percentage")
```

#### Observations

1.  For coffee table, about 50% of the products are more than \$ 90. It also has the highest percentage (20%) of products above \$160.
2.  For nightstand, sofa table, and living room table, about 60\~80% of the products are less than \$90.
3.  For the rest, about 90% of the products are less than \$90 (cheaper group).

### 1.2 Revenue

```{r message=FALSE}
ggplot(rev_df, aes(x=search_term, fill = rev_group)) + 
  geom_bar(stat="count", position = position_fill(reverse = TRUE)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n=10) ) + 
  coord_flip() +
  scale_fill_brewer(palette=8) +
  labs(title = "Revenue Groups of Search Terms", y = "percentage")
```

#### Observations

1.  Coffee table tends to have higher prices but lower sales and revenue. This is likely due to the fact that about 20% of the products are above \$160, which is quite expensive and also generates low revenue.
2.  In contrast, living room table which also has slightly higher price distribution does generate higher revenue.
3.  Nightstand generates higher revenue overall despite having lower prices.
4.  Sub-par revenue (\<50% in q3 and q4): sofa table, accent table.
5.  On-par revenue (\~50% in q3 and q4): coffee table, side table, end table
6.  Good revenue (\>50% in q3 and q4): nightstand, bedside table, living room table

```{r}
ggplot(rev_df %>% filter(price < 450 & revenue < 250000)) +
  geom_point(aes(x = price, y = revenue, color = search_term), alpha = 0.5, show.legend = FALSE) + facet_wrap(~search_term, ncol = 4)
```

```{r}
st_price <- PivotTable$new()
st_price$addData(rev_df)
st_price$addColumnDataGroups("search_term")
st_price$addRowDataGroups("price_group")
st_price$defineCalculation(calculationName = "total listings", summariseExpression="n()")
st_price$renderPivot()

```

```{r}
st_rev <- PivotTable$new()
st_rev$addData(rev_df)
st_rev$addColumnDataGroups("search_term")
st_rev$addRowDataGroups("rev_group")
st_rev$defineCalculation(calculationName = "total listings", summariseExpression="n()")
st_rev$renderPivot()
```

### 1.3 Product Dimension (Depth, Width, Height)

To measure the general "size" of an item, I used two metrics. The first is depth + width + height, the second is the volume. The reason I did not compare each individual dimension is two-fold. First, one dimension does not capture the overall size of an item Second, the order in which the dimension are given is not consistent across all items.

```{r}
ggplot(all_df %>% filter(!is.na(size_tier)), aes(x =search_term, y = girth_in, fill = search_term))  +
  geom_boxplot(outlier.shape = 8, show.legend = FALSE) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n=10)) +
  coord_flip() +
  labs(title ="Depth + Width + Height", y = 'D+W+H (inches)')
```

```{r}
ggplot(all_df %>% filter(!is.na(size_tier)), aes(x =search_term, y = vol_in, fill = search_term))  +
  geom_boxplot(outlier.shape = 8, show.legend = FALSE) + coord_flip() +
  labs(title ="Volume by Search Term", y = 'volume (inches)')
```

#### Observations

1.  Nightstand, side table, end table, beside table, and accent table tend to be on the smaller side.
2.  Coffee table, sofa table, and living room table are on the bigger side.
3.  For bigger items, go for living room table.
4.  For smaller items, go for nightstand, side table or bedside table.
5.  Living room table has a pretty wide range of dimensions

### 1.4 Package Size Tier

```{r}
ggplot(all_df, aes(x = search_term, fill = size_tier)) + geom_bar(position = 'fill') + coord_flip() +
  labs(title = 'Size Tier by Search Term', y = 'percentage')
```

#### Observations

1.  Most items are small oversize or large standard-size.

```{r}
rev_df %>% filter(!is.na(size_tier)) %>% group_by(size_tier) %>% 
  summarize(count = n(), 
            mean_rev = mean(revenue), 
            med_rev = median(revenue), 
            mean_price = mean(price),
            med_price = median(price)) %>% arrange(-med_rev)
```

```{r warning=FALSE}
ggplot(rev_df %>% filter(!is.na(size_tier) & size_tier %in% c('Large Standard-Size', 'Small Oversize', 'Medium Oversize') & search_term %in% c('1-coffee_table', '2-nightstand', '7-living_room_table'))) + 
  geom_point(aes(x = price, y = revenue, color = search_term), alpha = 0.5) + facet_grid(~size_tier) + xlim(0, 450) + ylim(0, 250000)
```

#### Observations

1.  Large Standard Size (the smallest size tier for these products) are all under \$100.

## 2. Page Comparisons

The products which are displayed on the first page of the search term generally has higher revenue.

```{r}
ggplot(rev_df %>% filter(revenue < 250000), 
       aes(x=factor(page), y=revenue, fill = page)) + 
  geom_boxplot(outlier.shape=8, show.legend = FALSE) + coord_flip() + 
  facet_wrap(~search_term, ncol = 4) + scale_fill_gradient(low="green", high="red") +
  scale_y_continuous(breaks = scales::pretty_breaks(n=3)) +
  labs(title = "Revenue Distribution by Page", x = "page")

```

#### Observations

1.  Overall, the first page generates higher revenue.
2.  Nightstand, which overall generates the high revenue, has similar revenue distribution between page 1 and 2.

So, what are some differences between products on the first and second page?

### 2.1 Price

```{r}
ggplot(all_df %>% filter(price < 450), 
       aes(x=factor(page), y=price, fill = page)) + 
  geom_boxplot(outlier.shape=8, show.legend = FALSE) + coord_flip() + 
  facet_wrap(~search_term, ncol = 4) + scale_fill_gradient(low="green", high="red") +
  labs(title = "Price Distribution by Page", x = "page")

```

#### Observations

1.  For coffee table, nightstand, side table, and end table, the first page shows more cheaper products.
2.  For coffee table, only 25% of the items on the first page are over \$100, whereas for the second page, 50% are over \$100.
3.  For living room table, the price on the first and second page are relatively similar. This could explain why despite both having higher price range, living room table still manages to have higher revenue.

### 2.2 Creation Date

```{r warning=FALSE}
ggplot(all_df, 
       aes(x=factor(page), y=creation_date, fill = page)) + 
  geom_boxplot(outlier.shape=8, show.legend = FALSE) + coord_flip() + 
  facet_wrap(~search_term, ncol = 4) + scale_fill_gradient(low="green", high="red") +
  labs(title = "Creation Date by Page", x = "page") 
```

#### Observations

1.  The first page doesn't show as many recent products as the second page, but not by a significant amount.
2.  For living room table and coffee table, the second page shows more products which were created after 2022.

### 2.3 Ratings

```{r}
# after this point, we will no longer be looking at each search term individually, so we will remove all duplicate items.
unique_df <- all_df[!duplicated(all_df$asin), ]

```

```{r message=FALSE, warning=FALSE}
ggplot(unique_df, 
       aes(x = ratings, fill = page)) + 
  geom_histogram(show.legend = FALSE) +
  facet_wrap(~page, ncol = 1) + scale_fill_gradient(low="green", high="red")+
  labs(title = "Ratings by Page", x = "page")
```

#### Observations

1.  Similar ratings distributions.

## 3. Color Group

### 3.1 Distribution

```{r}
ggplot(unique_df, aes(x=color_group)) + 
  geom_bar() + 
  geom_text(aes(label = after_stat(count)), stat="count", hjust = -0.1) +
  scale_y_continuous(breaks = scales::pretty_breaks(n=10) ) + 
  coord_flip() + 
  labs(title = "Color Groups")
```

#### Observations

1.  Top colors: Brown/black -\> brown -\> black -\> white -\> grey -\> grey/black (in desc. order of appearance)
2.  Top material: brown/black -\> wood + metal frame

```{r}
# median and mean of price, sales, revenue 
color_summary <- unique_df %>% filter(!is.na(sales)) %>% group_by(color_group) %>% 
  summarize('num_listings' = n(),
            'avg_price' = mean(price),
            'median_price' = median(price),
            'avg_rev' = mean(revenue),
            'median_rev' = median(revenue))

# color_summary %>% filter(num_listings > 10) %>% arrange(-median_rev)


```

### 3.2 Revenue

Let's look at the colors with at least 20 listings. This includes black, brown, brown/black, grey, grey/black, and white.

```{r warning=FALSE}
popular_color_names <- (color_summary %>% filter(num_listings > 20))$color_group
popular_colors <- unique_df %>% filter(!is.na(revenue) & color_group %in% popular_color_names)

ggplot(popular_colors %>% filter(!is.na(sales)), 
       aes(x=color_group, y=revenue, fill = color_group)) + 
  geom_boxplot(outlier.shape=8, show.legend = FALSE) + 
  ylim(0, 250000) +
  theme(axis.title.y = element_blank()) +
  coord_flip() +
  scale_fill_manual(values = c("black" = "black",
                                "brown"="brown",
                                "brown/black"="red",
                                'grey' = 'light grey',
                                'grey/black' = 'dark grey',
                                'white' = 'white')) + 
  labs(title = "Comparison of Revenue Distribution by color groups", subtitle = "Revenue < $250,000")
```

#### Observations

1.  Among the most popular items, grey and grey/black generate slightly higher revenue.
2.  Despite being the most popular colors, products in the brown and brown/black color group have relatively lower revenue.
3.  Grey/grey black have higher revenue.

### 3.3 Search Term

```{r}
ggplot(all_df, aes(x=color_group)) + 
  geom_bar() + 
  geom_text(aes(label = after_stat(count)), stat="count", hjust = -0.2, size = 2) +
  coord_flip() + facet_wrap(~search_term, ncol = 4) +
  labs(title = "Color Groups by Search Terms") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 7))
```

#### Observations

Compared to other search terms, living room table has a diverse range of products of different colors and materials (including plastic, glass, gold, etc.). These products tend to be more pricey but also generate higher revenue.

## Misc.

Living room table vs coffee table -- They both have similar ratings and size distribution. They both contain more higher priced items. Despite their similarities, coffee table generates low revenue in comparison. Why is that?

1.  Coffee table has the highest number of products above \$160. As established in report 1, products in this price range generally has low revenue.

2.  Living room table has a more diverse range of products in terms of size and colors/materials. In particular, it has What percentage of coffee table products above \$90 are shown in the first page? What about for living room table?

3.  The first page of coffee table shows a small percentage (34%) of the items in the \$90\~\$160 price bracket. In comparison, the first page of living room table shows almost 50% of the items in the \$90 \~ \$160 price bracket.

```{r}
# number of coffee table products above $90
a <- nrow(all_df %>% filter(price_group != '1' & search_term == '1-coffee_table'))

# number of coffee table products above $90 on the first page
b <- nrow(all_df %>% filter(price_group != '1' & search_term == '1-coffee_table' & page == 1))
print(paste("Percentage of 'coffee table' products above $90 shown on page 1:", b/a))
```

```{r}
# number of living room table products above $90
a <- nrow(all_df %>% filter(price_group != '1' & search_term == '7-living_room_table'))

# number of living room table products above $90 on the first page
b <- nrow(all_df %>% filter(price_group != '1' & search_term == '7-living_room_table' & page == 1))

print(paste("Percentage of 'living room table' products above $90 shown on page 1:", b/a))

```

Color breakdown of each search term. (Some products are duplicated, so ignore the total count for each color group. )

```{r}
color_st <- PivotTable$new()
color_st$addData(unique_df)
color_st$addColumnDataGroups("search_term")
color_st$addRowDataGroups("color_group")
color_st$defineCalculation(calculationName="Total Listings", summariseExpression="n()")
color_st$renderPivot()
```

```{r}
color_summary %>% filter(num_listings > 10) %>% arrange(-median_rev)

```

## 4. Revenue Groups

```{r}
ggplot(rev_df, aes(x=color_group)) + 
  geom_bar() + 
  geom_text(aes(label = after_stat(count)), stat="count", hjust = -0.2, size = 2) +
  coord_flip() + facet_wrap(~rev_group, ncol = 2) +
  labs(title = "Color Groups by Revenue Group") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 7))
```

```{r}
ggplot(popular_colors, aes(x=color_group, fill = rev_group)) + 
  geom_bar(position = position_fill(reverse=TRUE)) + 
  coord_flip() + scale_y_continuous(breaks = scales::pretty_breaks(n=10) ) +
  labs(title = "Revenue Breakdown of Popular Colors") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 7)) + scale_fill_brewer(palette = 8)
```

```{r}
ggplot(rev_df, aes(x=search_term, fill = search_term)) + 
  geom_bar() + 
  geom_text(aes(label = after_stat(count)), stat="count", hjust = -0.2, size = 2) +
  coord_flip() + facet_wrap(~rev_group, ncol = 2) +
  labs(title = "Search Terms by Revenue Group") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 7))
```

```{r message=FALSE}
ggplot(rev_df, aes(x=price_group, fill = rev_group)) + 
  geom_bar(stat="count", position = position_fill(reverse = TRUE)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n=10) ) + 
  coord_flip() +
  scale_fill_brewer(palette=8) +
  labs(title = "Revenue Breakdown of Price Groups", y = "percentage")
```
